\documentclass[a4paper,12pt]{article}
\usepackage[T1]{fontenc}    % Use T1 font encoding
\usepackage{lmodern}        % Use the Latin Modern font family

% for paragraph spacing
\usepackage{parskip}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=.9]{geometry}

% tabularx environment
\usepackage{tabularx}

% for lists within experience section
\usepackage{enumitem}
% spacing of bullet items in lists
\setlist[itemize]{leftmargin=1.5em, noitemsep, topsep=0pt}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

% custom \section
\usepackage{titlesec}

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

% Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0,0} % black links
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

%for social icons
\usepackage{fontawesome5}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

\begin{tabularx}{\linewidth}{@{} C @{}}
\vspace{-2em}
\Huge{Nebojša Kilibarda} \\[1pt]
\href{https://github.com/kilibarda4}{\raisebox{-0.05\height}\faGithub\ kilibarda4} \ $|$ \ 
\href{https://linkedin.com/in/nebojsakili}{\raisebox{-0.05\height}\faLinkedin\ nebojsakili} \ $|$ \ 
\href{mailto:nebojsakilibarda4@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ nebojsakilibarda4@gmail.com} \ $|$ \ 
\raisebox{-0.05\height}\faMobile \ +(469) 734 3716 \\
\end{tabularx}

%Interests/ Keywords/ Summary
\vspace{-0.6em}
\section{Objective}
Software Engineer with a rich skill set stemming from academic excellence and professional experience delivering scalable and secure software and firmware solutions in agile environments. A meticulous and thorough team player, I value cooperation, healthy competition and a team spirit.

\vspace{-0.6em}
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Current Stack:} Golang, React, Flutter, MySQL, MongoDB, AWS, Python, PyQt5 \\
\textbf{Languages:} Python, JavaScript, C, Golang, Dart, C++, Java, HTML/CSS, SQL, NoSQL \\
\textbf{Frameworks:} PyQt, Node.js, React JS, Swing, Tkinter, gensim \\
\textbf{Libraries:} Flask, Django, Pandas, NumPy, Matplotlib, Pytorch, Tensorflow \\
\textbf{Tech/Tools:} AWS, Docker, Kubernetes, Terraform, scikit, linux, Wireshark, \\ \hspace{6em} Agile/Scrum, Saleae, nRF SDK, Segger SDK, UNIX, Networking, Git
\end{tabularx}

%Experience
\vspace{-0.6em}
\section{Experience}

\begin{tabularx}{\linewidth}{@{}Xr@{}}
\textbf{Software Engineer Internship} & \hfill August 2024 - Present
\end{tabularx}
\textit{Ommo Technologies, Inc.}
\vspace{-0.4em}
\begin{itemize}
    \item Develop and maintain Python and PyQT GUIs for sensor manufacturers, significantly enhancing the efficiency and usability of sensor data handling software.
    \item Built CI/CD pipelines through GitHub Actions, \textbf{reducing development and deployment time} of GUIs by \textbf{25\%.}
    \item Re-architected software used in the manufacturing pipeline to replace serialized, one-at-a-time tasks with parallelized, asynchronous processes, which resulted in a \textbf{5x boost in throughput.}
\end{itemize}

\begin{tabularx}{\linewidth}{@{}Xr@{}}
\textbf{Embedded Software Engineer Internship} & \hfill May 2024 - August 2024
\end{tabularx}
\textit{Ommo Technologies, Inc.}
\vspace{-0.4em}
\begin{itemize}
    \item Wrote the firmware architecture for a custom PCB performing analog to digital conversion and integrated the device with the rest of the sensor management system through iterative work on the hardware and firmware of the NRF52840 board.
    \item Performed hardware testing with logic analyzers and oscilloscopes as well as unit testing and device calibration, \textbf{shortening development time approximately 20\%}.
\end{itemize}

%Education
\begin{tabularx}{\linewidth}{@{}Xr@{}}
\textbf{Easy-Med - Security, Privacy Assured IoMT} & \hfill May 2023 - July 2023
\end{tabularx}
\textit{National Science Foundation}
\vspace{-0.4em}
\begin{itemize}
    \item Trained on smart healthcare, received a \textbf{100\% evaluation} on core aspects of \textbf{cybersecurity and embedded programming} in the medical industry.
\end{itemize}

\vspace{-0.6em}
\section{Education}
\noindent
\begin{tabularx}{\linewidth}{@{}Xr@{}}
\textbf{Bachelor of Science, Computer Science} & August 2021 - May 2025 \\
\end{tabularx}
\vspace{0.2em}
University of Texas at Arlington \ GPA (3.72 / 4.0) \\
\textit{Upsilon Pi Epsilon Computing Honor's Society}

%Projects
\vspace{-0.6em}
\section{Projects}

%Animal Recognition
\vspace{-0.4em}
\href{https://github.com/kilibarda4/nyse-tracker}
{\textbf{NYSE Tracker}} \ \textit{React JS, Python Django, Docker, Google Cloud Platform}
\begin{itemize}
\vspace{-0.4em}
    \item Developed a cloud-native full-stack application using React and Django that helps traders get \textbf{real-time} market updates on user-defined watch lists and holdings.
    \item Leveraged Cloud Functions and Pub/Sub to continuously monitor real-time stock prices and trigger notifications in response to user-defined alerts.
\end{itemize}

\vspace{-0.4em}
\href{https://github.com/kilibarda4/pos-tagger-Maithili}
{\textbf{Part Of Speech Tagger for Maithili}} \ \textit{Python, scikit-learn, PyTorch}
\begin{itemize}
\vspace{-0.4em}
    \item Built a part of speech tagger for the low resource Maithili language by fine tuning BERT transformer.
    \item Achieved an \textbf{F1 score of 0.89} on a limited dataset by adding a Conditional Random Fields layer.
\end{itemize}

\vfill
\end{document}
